Sampling requirements to detect ecosystem change

### 2020-03-31 R/supp_material.Rmd
need to commit before push
first edits of the day to supp material

# Additional text

We first detect the ``true" changepoint of a full length time series with the function _e.divisive_ in the R package _ecp_ [@James2019]. We focus on the changepoint with the largest magnitude, altough this package allows lower order changepoint detection as well (Fig. \ref{fig:case_study_other_changepoints}). We then subsample the full time series [@White2020] with different numbers of subsamples and different sampling approaches. For each sampling approach, we wrote a custom function:

@@

@@

>>>>

# Additional methods

We first detect the ``true" changepoint of a full length time series with the function _e.divisive_ in the R package _ecp_ [@James2019]. We focus on the changepoint with the largest magnitude, altough this package allows detection of further changepoints as well (Fig. \ref{fig:case_study_other_changepoints}). We then subsample the full time series [@White2020] with different numbers of subsamples and different sampling approaches. For each sampling approach, we wrote a custom function:

@@

Each function works with two types of input: vector and matrix. If the input is a matrix, the user must change the default argument *is_vector* to *FALSE*. The matrix is transformed to independent vectors using Detrented Correspondance Analysis [@hill_detrended_1980], and a single axis on which changepoint analysis is run is chosen with the argument *DCA_axis* (default to 1, for first component).

@@

## Case study: biomass

```{r echo=FALSE, eval=T,message=FALSE, warning=FALSE, fig.width = 7.2, fig.height= 3,fig.cap='Distance to real changepoint in biomass per total number of samples analyzed, following (a) random sampling, (b) regular sampling, and (c) iterative sampling. Total number of samples was set between 5 and 30, out of the 74 initial time series.  \\label{fig:case_study_number_sample}'}
#investigating species average biomass
vr_count <- rowSums(vr[,-1])
myoutput_count <- NULL
j=3
for (i in 5:30) {
  vrsub <- sample_regular(vr_count, i, input_vector = T, messages = F)
  myoutput_count <- c(myoutput_count, vrsub$method, vrsub$final_n, vrsub$changepoint_all$order.found[j], length(vrsub$changepoint_all$estimates)-2)
  vrsub <- sample_random(vr_count, i, input_vector = T, messages = F)
  myoutput_count <- c(myoutput_count, vrsub$method, vrsub$final_n, vrsub$changepoint_all$order.found[j], length(vrsub$changepoint_all$estimates)-2)
  vrsub <- sample_iterative(vr_count, i, input_vector = T, messages = F)
  myoutput_count <- c(myoutput_count, vrsub$method, vrsub$final_n, vrsub$changepoint_all$order.found[j], length(vrsub$changepoint_all$estimates)-2)
  vrsub <- sample_iterative(vr_count, i, input_vector = T, messages = F, n2 = 6)
  myoutput_count <- c(myoutput_count, vrsub$method, vrsub$final_n, vrsub$changepoint_all$order.found[j], length(vrsub$changepoint_all$estimates)-2)
  vrsub <- sample_iterative(vr_count, i, input_vector = T, messages = F, n2 = 7)
  myoutput_count <- c(myoutput_count, vrsub$method, vrsub$final_n, vrsub$changepoint_all$order.found[j], length(vrsub$changepoint_all$estimates)-2)
}

myoutput <- read.table(paste0(getwd(),"/Output/output_changepoint_varese_biomass.txt"))
myoutput$method <- factor(myoutput$method, levels=c('Random', 'Regular', 'Iterative'))
myoutput$diff_real <- abs(myoutput$diff_real)

# Plot
p1 <-
  ggplot(myoutput[myoutput$target_cpt==1 & myoutput$n2_init == 5,], aes(final_n,diff_real)) + 
  geom_hline(aes(yintercept=0), col=adjustcolor("black", alpha.f = .4)) + 
  geom_point(alpha = .3) +
  facet_wrap(~method,
             labeller = label_glue('{.l}. {method} sampling ')) + 
  theme_bw() +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        strip.background = element_rect(colour="transparent", fill="transparent"),
        strip.text.x = element_text(angle = 0, hjust = 0)) +
  labs(x="Total number of samples analyzed", y="Distance to real changepoint")

p1

(Fig. \ref{fig:case_study_number_sample_change_biomass})
